Investigating the change of Toronto crime rates from 2014-2023

### 2024-01-25 Output/paper.qmd
digits changed

The analysis will be using R [@citeR] and various R packages such as "tidyverse" [@citeTidyverse], "ggplot2" [@citeGgplot2], "knitr" [@citeKnitr], "kableExtra" [@citeKableExtra], and "dplyr" [@citeDplyr], the dataset is cleaned and transformed to a table, since the year variable is in the columns, the table only displays the 2023 data for assault, break enter, homicide, robbery, shooting, and bike theft as an example. Moreover, the digits are to the 1 decimal place (see @tbl-exampleneighbourhoodcrimerates).

@@

# create a table with selected columns
example_tbl <- 
  head(example_data) |>
  kable(
    col.name = c("Id", "Assault", "BreakEnter", "Homicide", "Robbery", "Shooting", "BikeTheft"),
    digits = 1,
    booktabs = TRUE
  )

@@

# Proceed with creating the table using kable
kable_table <- kable(wexford_table, "latex", booktabs = TRUE, digits = 1, longtable = TRUE) |>
  kable_styling(latex_options = c("repeat_header"))

@@

# Proceed with creating the table using kable
kensington_kable_table <- kable(kensington_table, "latex", booktabs = TRUE, digits = 1, longtable = TRUE) |>
  kable_styling(latex_options = c("repeat_header"))

>>>>

The analysis will be using R [@citeR] and various R packages such as "tidyverse" [@citeTidyverse], "ggplot2" [@citeGgplot2], "knitr" [@citeKnitr], "kableExtra" [@citeKableExtra], and "dplyr" [@citeDplyr], the dataset is cleaned and transformed to a table, since the year variable is in the columns, the table only displays the 2023 data for assault, break enter, homicide, robbery, shooting, and bike theft as an example see @tbl-exampleneighbourhoodcrimerates.

@@

# create a table with selected columns
example_tbl <- 
  head(example_data) |>
  kable(
    col.name = c("Id", "Assault", "BreakEnter", "Homicide", "Robbery", "Shooting", "BikeTheft"),
    booktabs = TRUE
  )

@@

# Proceed with creating the table using kable
kable_table <- kable(wexford_table, "latex", booktabs = TRUE, longtable = TRUE) |>
  kable_styling(latex_options = c("repeat_header"))

@@

# Proceed with creating the table using kable
kensington_kable_table <- kable(kensington_table, "latex", booktabs = TRUE, longtable = TRUE) |>
  kable_styling(latex_options = c("repeat_header"))
